Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-10 paper/disc20clustering.tex
wip

This problem is known as the dynamic balanced graph partitioning problem introduced by Avin et al. \cite{repartition-disc, sidma-arxiv} at DISC 2016. A special variant of the general problem has later been studied by Henzinger et al. \cite{sigmetrics19_partitioning} at SIGMETRICS 2019.
We will refer to the latter as the learning model.

@@

\noindent
\textbf{Resource augmentation.}
The majority of work on Online Balanced Partitioning so far \cite{repartition-disc,sigmetrics19_partitioning} focuses on the scenario with resource augmentation, where the clusters of \ALG are larger than the clusters of \OPT.
We can adjust our construction to show a lower bound of $\Omega(\ell)$ for resource augmentation.

@@

Finally, we note the possibility of improvement. The algorithm CREP~\cite{repartition-disc} requires $(2+\epsilon)$-augmentation to guarantee the competitive ratio independent of $\ell$.

>>>>

This problem is known as the dynamic balanced graph partitioning problem and was introduced by Avin et al. \cite{repartition-disc, sidma-arxiv} at DISC 2016. A special variant of the general problem has later been studied by Henzinger et al. \cite{sigmetrics19_partitioning} at SIGMETRICS 2019.
We refer to the latter as the learning model.

@@

\noindent
\textbf{Resource augmentation.}
The majority of work on Online Balanced Partitioning so far \cite{repartition-disc,sigmetrics19_partitioning} focuses on the scenario with resource augmentation, where the clusters of an online algorithm are larger than the clusters of the offline optimal algorithm that we compare the performance to.
We can adjust our construction to show a lower bound of $\Omega(\ell)$ for resource augmentation.

@@

Finally, we note the possibility of improvement. The algorithm CREP~\cite{repartition-disc} requires $(2+\epsilon)$-augmentation to guarantee the competitive ratio independent of $\ell$.
In contrast, our construction shows that the linear term $\ell$ is inevitable if the augmentation is smaller than $1+1/3$.
